---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dhhstheme

<!-- badges: start -->
<!-- badges: end -->

*This package is under development and subject to change substantially.* 
Use for exploration but not yet for production. 

This package is designed to make DHHS-styled charts with the `ggplot2` R package.

It is currently maintained by Will Mackey.

Please file an issue to report bugs or request features at: 

## Installation

You can install this package from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("wfmackey/dhhstheme")
```
## Example


```{r example}
library(dhhstheme)
library(tidyverse)

mtcars %>%
  ggplot(aes(hp, wt,
             colour = factor(cyl))) +
  geom_point(size = 6, alpha = .8) +
  theme_dhhs() +
  dhhs_colour_manual(3) +
  labs(title = "A plot with DHHS colours",
       subtitle = "y-axis label",
       y = NULL,
       x = "x-axis label",
       colour = "Legend title",
       caption = "Sources and notes.")

dhhs_save("data-raw/ouput/colours.png", type = "half")

```
