---
title: "Using {dhhstheme}"
author: "Will Mackey"
date: "13/10/2020"
output: 
  html_document:
    theme: paper
    highlights: kate
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

devtools::load_all()
```

# The `dhhstheme` package

The `dhhstheme` package is designed to make it easier to generate DHHS-style charts using the `ggplot2` package in R.


# Set up

The package is hosted on Github. To install a package from Github, use the `install_github()` function from the `remotes` package:

```{r install, eval=FALSE}
install.packages("remotes")
remotes::install_github("wfmackey/dhhstheme")
```

Then load the package, along with the `tidyverse` package that contains `ggplot2` and other data-manipulation tools:

```{r library, message = FALSE, warnings = FALSE}
library(dhhstheme)
library(tidyverse)
```

The package contains some COVID-19 data from [Our World in Data](https://ourworldindata.org/coronavirus) for demonstrations. This is  loaded with the package in `owid_sample`: 


```{r data}
glimpse(owid_sample)
```



## A basic bar chart using `theme_dhhs`

```{r base_col}
owid_sample %>% 
  filter(country == "Australia") %>% 
  ggplot(aes(date, new_cases)) + 
  geom_col(width = 1)
```


To add the DHHS theme, add `theme_dhhs`:

```{r theme_col}
owid_sample %>% 
  filter(country == "Australia") %>% 
  ggplot(aes(date, new_cases)) + 
  geom_col(width = 1) +
  theme_dhhs()
```


You can use the pre-set DHHS colours to `fill` the plot:

```{r theme_col2}
owid_sample %>% 
  filter(country == "Australia") %>% 
  ggplot(aes(date, new_cases)) + 
  geom_col(width = 1,
           fill = dhhs_teal) +
  theme_dhhs()
```


Finally, adding titles and labels:

```{r theme_col3}
aus_cases <- owid_sample %>% 
  filter(country == "Australia") %>% 
  ggplot(aes(date, new_cases)) + 
  geom_col(width = 1,
           fill = dhhs_teal) +
  theme_dhhs() +
  labs(title = "Australia's second wave peaked in August",
       subtitle = "Daily COVID-19 cases in Australia",
       x = NULL,
       y = NULL,
       caption = "Source: Our World in Data (ourworldindata.org/coronavirus).")

aus_cases
```

## Saving a bar-chart

The `dhhs_save` function

```{r save_col, message = FALSE}
dhhs_save(file_path = "data-raw/aus_cases.png", 
          plot_object = aus_cases)
```

By default, this will save

## Adding `theme_dhhs` and labels







# misc



```{r base_line}
p_base_line <- owid_sample %>% 
  ggplot(aes(date, total_cases_per_million,
             colour = country)) + 
  geom_line()

p_base_line
```

```{r theme_line}
p_base_line + 
  theme_dhhs() + 
  labs(title = "United States leads the way",
       subtitle = "Cumulative COVID-19 cases per million population",
       x = "Date",
       y = NULL,
       colour = "Country:")
```



```{r base_point}

p_base_point <- owid_sample %>% 
  filter(start_of_month) %>% 
  ggplot(aes(total_cases_per_million, total_deaths_per_million,
             colour = country)) + 
  geom_point(size = 4, alpha = .8) + 
  scale_x_log10() + 
  scale_y_log10()

p_base_point
```


